### 2021-07-27 paper/paper.tex
update TODO notes as discussed in the Trixi meeting

% TODO: Update Trixi version below
As of version v0.3.50 (July 2021), \trixi comes with the following features.
\begin{itemize}
  \item 1D, 2D, and 3D simulations on line/quad/hex/simplex meshes
  \begin{itemize}
    \item Cartesian and curvilinear meshes
    \item Conforming and non-conforming meshes
    \item Structured and unstructured meshes
    \item Hierarchical quadtree/octree grid with adaptive refinement
  \end{itemize}

  \item High-order nodal and modal discontinuous Galerkin methods
  \begin{itemize}
    \item Kinetic energy preserving and entropy-stable methods
    \item Entropy-stable shock-capturing
    \item Positivity-preserving limiting
  \end{itemize}

@@

Since functions are first-class citizens in Julia, they can be passed around
and used efficiently. Thus, everything that acts like a function can be used
in \trixi, \eg, to define initial/boundary conditions. While such a flexibility
is not too uncommon, two-point numerical fluxes are also just functions with a
specified signature. Thus, users can implement numerical fluxes in their
own code and they will work and be as efficient as if they were implemented
directly in \trixi.

@@

@@

@@

\subsubsection{External C libraries can be integrated relatively easily}

@@

@@

\todo{ % TODO
\begin{itemize}
  \item Full paper: 5--10 pages
  \item Prepare repro repo including scripts for \trixi and FLUXO
  \item The title of our talk at JuliaCon is
  ``Adaptive and extendable numerical simulations with Trixi.jl''.
  Shall we use something like
  ``Adaptive high-order numerical simulations of hyperbolic PDEs with Trixi.jl:
  A case study of Julia for scientific computing'' for this paper?
  \item Restructure non-conservative stuff and add MHD benchmarks
  \item Shall we re-create the schematic overview in tikz?
  \item Shall we compare \trixi to other open source frameworks such as MFEM, NGSolve, DealII, DUNE, FENICS, Firedrake, ClawPack, ...?
  \item Are there other aspects we should discuss?
\end{itemize}
\begin{quote}
  Compared to an extended abstract, a full paper presents more of the background
  and context motivating the work. It compares the work to other approaches taken
  in the field and gives some additional insights on the conference contribution.
  Use cases back up the work by showing how it can be used.
\end{quote}}

>>>>

% TODO: Update Trixi version below
As of version v0.3.50 (July 2021), \trixi comes with the following features.
\begin{itemize}
  \item 1D, 2D, and 3D simulations on line/quad/hex/simplex meshes
  \begin{itemize}
    \item Cartesian and curvilinear meshes
    \item Conforming and non-conforming meshes
    \item Structured and unstructured meshes
    \item Hierarchical quadtree/octree grid with adaptive refinement
    \item Forests of qudtrees/octrees with \texttt{p4est} \cite{burstedde2011p4est}
          via P4est.jl\footnote{\url{https://github.com/trixi-framework/P4est.jl}}
  \end{itemize}

  \item High-order discontinuous Galerkin methods
  \begin{itemize}
    \item Kinetic energy preserving and entropy-stable methods
    \item Entropy-stable shock-capturing
    \item Positivity-preserving limiting
  \end{itemize}

@@

Since functions are first-class citizens in Julia, they can be passed around
and used efficiently. Thus, everything that acts like a function can be used
in \trixi, \eg, to define initial/boundary conditions. While the flexibility
to change initial/boundary conditions
is not too uncommon, two-point numerical fluxes are also just functions with a
specified signature. Thus, users can implement numerical fluxes in their
own code and they will work and be as efficient as if they were implemented
directly in \trixi.

@@

\todo{TODO: Mention multiple dispatch} %TODO

@@

\todo{TODO: Be careful how to formulate this, be more neutral} %TODO

\todo{TODO: Point out that both codes have features the other ones does not} %TODO

@@

\subsubsection{External libraries can be integrated relatively easily}

@@

\todo{TODO: Mention also Fortran libraries/codes (KROME, HOHQMesh)} %TODO

@@

\todo{ % TODO
\begin{itemize}
  \item Full paper: 5--10 pages
  \item Prepare repro repo including scripts for \trixi and FLUXO
  \item The title of our talk at JuliaCon is
  ``Adaptive and extendable numerical simulations with Trixi.jl''.
  Shall we use something like
  ``Adaptive high-order numerical simulations of hyperbolic PDEs with Trixi.jl:
  A case study of Julia for scientific computing'' for this paper?
  \item Restructure non-conservative stuff and add MHD benchmarks
  \item Shall we re-create the schematic overview in tikz?
  \item Shall we compare \trixi (in terms of structure, not performance!)
        to other open source frameworks such as MFEM,
        NGSolve, DealII, DUNE, FENICS, Firedrake, ClawPack, ...? Definitely not
        explicitly to not make people angry, but maybe implicitly without
        mentioning their names?
        \begin{itemize}
          \item Everything in Julia, not a two language problem!
          \item Other things? Gregor will think about it!
        \end{itemize}
  \item Are there other aspects we should discuss?
  \item Check affiliations
  \item Maybe include some cool pictures? Give a flavor of the kind of simulations
        you can do with \trixi? Pictures trigger people! For example after the
        list of main features?
  \item Summary of community, collaborators, and users: GitHub statistics, contributors,
        Vikram and Chandrashekar, Steven Frankel and Philipp Öffner (maybe), ...
        Related to the relatively large number of students!
        $\to$ Jesse will make a PR!
  \item A simple example where we really use multiple dispatch?
        \begin{itemize}
          \item Just pass functions around
          \item Dispatch on parameters of DG struct
        \end{itemize}
\end{itemize}
\begin{quote}
  Compared to an extended abstract, a full paper presents more of the background
  and context motivating the work. It compares the work to other approaches taken
  in the field and gives some additional insights on the conference contribution.
  Use cases back up the work by showing how it can be used.
\end{quote}}
